Clustering based on probability distributions with application on residential customers

### 2021-10-08 main.Rmd
adding application first methods story

### Characteristics of raw data

@@

First, we select the customers which do not have any implicit missing values and filtered their data for the year 2013. From this set, we randomly sample a set of 600 customers. Then we removed customers for which any of the hod, moy and wkndwday is a clash. We further removed customers for which the deciles of the energy consumption is of the same value. Finally, we are left with 356 customers from which we wanted to do instance selection. Since this is unlabeled data, there is no way to do external validation of our methodologies. Thus, we chose this way to see how well our methodology works in a cleaner data set as this one to classify customers who have similar behavior across all significant granularities. Next we select 4 customers which are far apart from each other and 6 customers which are lying closest in distance to each of these 4 customers. These selection was done using the granularity hod. When we use our methodologies, it is based on all significant granularities and not only hod, but if hod is significant we can expect that the grouping would be similar to how we have initially chosen the set of customers. This is process is similar to instance-wise classfication methods.By this instancewise discriminative learning, instances can reasonably distribute in the representation space, which reveals their similarities. In
order to further improve visual representations, we propose a
dual-level progressive similar instance selection (DPSIS) method
to build a bridge from instance to class by selecting similar
instances (neighbors) for each instance (anchor) and treating the
anchor and its neighbors as the same class.

Fig \ref{fig:data-heatmap-hod}, \ref{fig:} and \ref{fig:} shows the distribution of 24 customers across hour-of-day, month-of-year and wknd-wday respectively. Every row in \ref{fig:} shows different shapes across hour-of-day and across columns show similar shapes for each row. We use our methodology to see if the customers are allocated to same group have similar shapes across one or more significant granularity.

@@

```{r data-heatmap-hod, fig.cap="The distribution of electricity demand for the selected 24 customers across hour-of-day. The median is represented by a line and shaded region represents the area between $25^{th}$ and $75^{th}$ percentile. According to our instance selection method, each row represnts a distinct shape of daily load, and all customers in the same row should have similar daily profile.After clustering these consumers, all customers with the same colour represent the same group. Except for customer id 8269176, there is unanimity across design and groups. Even though their daily form resembles Group 2, our clustering approach places them in Group 3 (which is design 4 in our case). Because our method uses hod, moy, and wkndwday, there may be some mismatches depending on only one variable."}

@@

data_heatmap_hod %>% 
  mutate(customer_id = as.character(customer_id)) %>% 
  left_join(cluster_result, by = c("customer_id" = "id")) %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`,
                  group=customer_id,
                  fill = as.factor(group)),
              alpha = 0.5) +
  geom_line(aes(y = `50%`,
                group=customer_id, 
                color = as.factor(group)), size = 1) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) +
    theme_bw() +
   theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") +
  ylab("demand (in Kwh)")  + 
  theme(panel.spacing =unit(0, "lines")) + 
  theme(axis.text.x = element_text(angle=90, hjust=1, size = 7)) + theme(legend.position = "bottom")+ 
  #theme() strip.text = element_text(size = 8, margin = margin(b = 0, t = 0)))+
  theme(plot.margin = margin(0, 0, 0, 0, "cm") ) +
  scale_x_discrete(breaks = seq(0,23, 4)) +
  scale_color_manual(legend_title, values = c("#E69F00", "#009E73","#0072B2", "#D55E00")) +
  scale_fill_manual(legend_title, values = c("#E69F00", "#009E73","#0072B2", "#D55E00")) +
  xlab("hour-of-day")
```
```{r data-heatmap-moy, fig.cap = "The distribution of electricity demand for the selected 24 customers across month-of-year. The median is represented by a line and shaded region represents the area between 25^{th} and 75^{th} percentile. The clustering leads to customers with similar shape across month-of-year with some exceptions. This is natural in a clus"}

@@

data_heatmap_moy %>% 
  mutate(customer_id = as.character(customer_id)) %>% 
  left_join(cluster_result, by = c("customer_id" = "id")) %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=customer_id), fill = "lightblue") +
  geom_line(aes(y = `50%`, group=customer_id, color = as.factor(group)), size = 1) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) +
    theme(strip.text = element_text(size = 7, margin = margin(b = 0, t = 0))) + xlab("month-of-year") + ylab("demand (in Kwh)")  + theme_bw() + theme(panel.spacing =unit(0, "lines")) + theme(axis.text.x = element_text(angle=90, hjust=1, size = 7)) + theme(legend.position = "bottom")+ theme(
    strip.text = element_text(size = 8, margin = margin(b = 0, t = 0)))+
  theme(plot.margin = margin(0, 0, 0, 0, "cm") )
```

@@

```{r data-heatmap-hod-group, fig.cap="The distribution of electricity demand for the clusters across hour-of-day. The median is represented by a line and the shaded region represents the area between 25^{th} and 75^{th} percentile. The first cluster is characterised by high comsumption in early morning hours and late night hours. The second cluster should be the most common type of daily profile characterised by a smaller morning and higher evening peak. The third cluster corresponds to two equal peaks and the last one corresponds to only distinct evening peaks."}

@@

data_heatmap_hod_group %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`,
                  group=group,
                  fill = as.factor(group)),
              alpha = 0.5) +
  geom_line(aes(y = `50%`,
                group=group, 
                color = as.factor(group)), size = 1)+
  facet_wrap(~group, 
             scales = "free_y",  nrow = 4) + 
              #labeller = labeller(xfacet = c(`1` = "Group 2", `2` = "Group 4",`3` = "Group 1",`4` = "Group 3"))
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)") + 
  theme_bw() + 
  theme(panel.spacing =unit(0, "lines")) + theme(axis.text.x = element_text(angle=90, hjust=1, size = 7)) +
  scale_x_discrete(breaks = seq(1, 24, 3))+ 
  #theme(strip.text = element_text(size = 8, margin = margin(b = 0, t = 0)))+
  theme(plot.margin = margin(0, 0, 0, 0, "cm")) +
  scale_fill_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00"))+
  scale_color_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00"))+
  theme(legend.position = "bottom")

@@

Characterization of clusters is the final stage of a cluster analysis.
However, if we are convinced that we have identified a collection of clusters that can be distinguished from one another, we should intend to characterise them more formally, both statistically and qualitatively. We quantify them by producing statistics for each variable. We may look at the findings in graphs, and enhance our qualitative descriptions of the groupings.

We discover 4 qualitative clusters of varying shapes in the distribution of all consumers in a group. Group-1 includes consumers who work 9-5, get up and conduct morning activities from 7-10am, and then depart. Then they return home in the evening to cook supper and perform other activities, giving the evening a greater peak than the morning. Group 2 is the group that rushes out of the house in the morning to get to work. They only return at night and do all activities at night, so there is no morning peak. The third one has a strong early morning and late night hours. These consumers may be flexible students or elderly retirees who are night owls. Presence of children or stay-at-home parents is indicated by Group-4's almost equivalent morning, afternoon and evening peaks. All of this may be validated with further information about the customer.

@@

data_heatmap_moy_group %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=group, fill = as.factor(group))) +
  geom_line(aes(y = `50%`, group=group)) +
  facet_wrap(~group, 
             scales = "free_y", 
             labeller = "label_value",
             nrow = 4) +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("month-of-year") + ylab("demand (in Kwh)") + theme_bw() + theme(panel.spacing =unit(0, "lines")) + theme(axis.text.x = element_text(angle=90, hjust=1, size = 7)) + theme(
    strip.text = element_text(size = 8, margin = margin(b = 0, t = 0)))+
  theme(plot.margin = margin(0, 0, 0, 0, "cm") )

```
The clusters across month-of-year shows that cluster 2 uses electricity in summer.

@@

data_heatmap_wkndwday %>% 
  mutate(customer_id = as.character(customer_id)) %>% 
  left_join(cluster_result, by = c("customer_id" = "id")) %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=customer_id), fill = "lightblue") +
  geom_line(aes(y = `50%`, group=customer_id, color = as.factor(group)), size = 1) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) +
    theme(strip.text = element_text(size = 7, margin = margin(b = 0, t = 0))) + xlab("wknd_wday") + ylab("demand (in Kwh)")  + theme_bw() + theme(panel.spacing =unit(0, "lines")) + theme(axis.text.x = element_text(angle=90, hjust=1, size = 7)) + theme(legend.position = "bottom")+ theme(
    strip.text = element_text(size = 8, margin = margin(b = 0, t = 0)))+
  theme(plot.margin = margin(0, 0, 0, 0, "cm") )

@@

```{r data-heatmap-wkndwday-group}

@@

data_heatmap_wkndwday_group %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=group, fill = as.factor(group))) +
  geom_line(aes(y = `50%`, group=group)) +
  facet_wrap(~group, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 4) +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("wknd_wday") + ylab("demand (in Kwh)") + theme_bw() + theme(panel.spacing =unit(0, "lines")) + theme(axis.text.x = element_text(angle=90, hjust=1, size = 7)) + theme(
    strip.text = element_text(size = 8, margin = margin(b = 0, t = 0)))+
  theme(plot.margin = margin(0, 0, 0, 0, "cm") )

>>>>

## Characteristics of raw data

@@

First, we select the customers which do not have any implicit missing values and filtered their data for the year 2013. From this set, we randomly sample a set of 600 customers. Then we removed customers for which any of the hod, moy and wkndwday is a clash. We further removed customers for which the deciles of the energy consumption is of the same value. Finally, we are left with 356 customers from which we wanted to do instance selection. Since this is unlabeled data, there is no way to do external validation of our methodologies. Thus, we chose this way to see how well our methodology works in a cleaner data set as this one to classify customers who have similar behavior across all significant granularities. Next we select 4 customers which are far apart from each other and 6 customers which are lying closest in distance to each of these 4 customers. These selection was done using the granularity hod. When we use our methodologies, it is based on all significant granularities and not only hod, but if hod is significant we can expect that the grouping would be similar to how we have initially chosen the set of customers. This procedure is analogous to instance-wise classfication methods. Instances may be distributed in the representation space in a reasonable manner, revealing their similarities, using this instance wise discriminative learning. A dual-level progressive similar instance selection (DPSIS) approach could also be used that selects similar instances (neighbours) for each instance (anchor) and treats the anchor and its neighbours as the same class.

<!-- Fig \ref{fig:data-heatmap-hod}, \ref{fig:} and \ref{fig:} shows the distribution of 24 customers across hour-of-day, month-of-year and wknd-wday respectively. Every row in \ref{fig:} shows different shapes across hour-of-day and across columns show similar shapes for each row. We use our methodology to see if the customers are allocated to same group have similar shapes across one or more significant granularity. -->

@@

```{r data-heatmap-hod-new, fig.cap="The distribution of electricity demand for the selected 24 customers across hour-of-day. The median is represented by a line and shaded region represents the area between $25^{th}$ and $75^{th}$ percentile. According to our prototype selection method, each row represents a distinct shape of daily load, and all customers in the same row should have similar daily profile.After clustering these consumers, all customers with the same colour represent the same group. Except for customer id 8269176, there is unanimity across design and groups. Even though their daily form resembles Group 2, our clustering approach places them in Group 3 (which is design 4 in our case). Because our method uses hod, moy, and wkndwday, there may be some mismatches depending on only one variable."}

@@

data_heatmap_hod %>% 
  mutate(customer_id = as.character(customer_id)) %>% 
  left_join(cluster_result, by = c("customer_id" = "id")) %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`,
                  group=customer_id,
                  fill = as.factor(group)),
              alpha = 0.5) +
  geom_line(aes(y = `50%`,
                group=customer_id, 
                color = as.factor(group)), size = 1) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) +
    theme_bw() +
   theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) +
    theme(strip.text = element_text(size = 10,
                                    margin = margin(b = 0, t = 0))) +
  ylab("demand (in Kwh)")  + 
  theme(panel.spacing =unit(0, "lines")) + 
  theme(axis.text.x = element_text(angle=90, hjust=1, size = 7)) + theme(legend.position = "bottom")+ 
  #theme() strip.text = element_text(size = 8, margin = margin(b = 0, t = 0)))+
  theme(plot.margin = margin(0, 0, 0, 0, "cm") ) +
  scale_x_discrete(breaks = seq(0,23, 4)) +
  scale_color_manual(legend_title, values = c("#E69F00", "#009E73","#0072B2", "#D55E00")) +
  scale_fill_manual(legend_title, values = c("#E69F00", "#009E73","#0072B2", "#D55E00")) +
  xlab("hour-of-day") 
```

```{r data-heatmap-moy, fig.cap = "The distribution of electricity demand for the selected 24 customers across month-of-year. The median is represented by a line and shaded region represents the area between $25^{th}$ and $75^{th}$ percentile. Intriguingly, customer id 8269176 appears to be in the appropriate group (Group 3) because its monthly profile is more similar to Group 3 than Design 4. So, while our clustering approach failed to place the customer in the correct hour-of-day group, it did so for month-of-year. When contrasting the moy to hod profile, there are greater behavioural differences across customers within a group."}

@@

data_heatmap_moy %>% 
  mutate(customer_id = as.character(customer_id)) %>% 
  left_join(cluster_result, by = c("customer_id" = "id")) %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, 
                  group=customer_id, 
              fill = as.factor(group)), alpha = 0.5) +
  geom_line(aes(y = `50%`, group=customer_id, color = as.factor(group)), size = 1) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) +
    theme(strip.text = element_text(size = 10,
                                    margin = margin(b = 0, t = 0))) + xlab("month-of-year") +
  ylab("demand (in Kwh)")  +
  theme_bw() +
   theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) + 
  theme(panel.spacing =unit(0, "lines")) + theme(axis.text.x = element_text(angle=90, hjust=1, size = 7)) + theme(legend.position = "bottom")+ theme(
    strip.text = element_text(size = 8, margin = margin(b = 0, t = 0)))+
  theme(plot.margin = margin(0, 0, 0, 0, "cm") )+
  scale_color_manual(legend_title, values = c("#E69F00", "#009E73","#0072B2", "#D55E00")) +
  scale_fill_manual(legend_title, values = c("#E69F00", "#009E73","#0072B2", "#D55E00")) +
  xlab("month-of-year") +  theme(axis.text.x = element_text(size=5))
```

@@

```{r data-heatmap-hod-group}

@@

hod_group <- data_heatmap_hod_group %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`,
                  group=group,
                  fill = as.factor(group), alpha = 0.5),
              alpha = 0.5) +
  geom_line(aes(y = `50%`,
                group=group, 
                color = as.factor(group)), size = 1)+
  facet_wrap(~group, 
             scales = "free_y",  
             nrow = 4) + 
              #labeller = labeller(xfacet = c(`1` = "Group 2", `2` = "Group 4",`3` = "Group 1",`4` = "Group 3"))
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + 
  ylab("demand (in Kwh)") + 
  theme_bw() +
   theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())+
  theme(panel.spacing =unit(0, "lines")) + 
  theme(axis.text.x = element_text(angle=90, hjust=1, size = 7)) +
  scale_x_discrete(breaks = seq(1, 24, 3))+ 
  #theme(strip.text = element_text(size = 8, margin = margin(b = 0, t = 0)))+
  theme(plot.margin = margin(0, 0, 0, 0, "cm")) +
   scale_color_manual(legend_title, values = c("#E69F00", "#009E73","#0072B2", "#D55E00")) +
  scale_fill_manual(legend_title, values = c("#E69F00", "#009E73","#0072B2", "#D55E00")) + 
  theme(legend.position = "bottom")

@@

Characterization of clusters is the final stage of a cluster analysis.
If we are convinced that we have identified a collection of clusters that can be distinguished from one another, we should intend to characterize them more formally, both statistically and qualitatively. We quantify them by producing statistics for each variable. We may look at the findings in graphs, and enhance our qualitative descriptions of the groupings.

\noindent We discover 4 qualitative clusters of varying shapes in the distribution of all consumers in the first panel of Figure \ref{fig:combined}. Group-1 includes consumers who work 9-5, get up and conduct morning activities from 7-10am, and then depart. Then they return home in the evening to cook supper and perform other activities, giving the evening a greater peak than the morning. Group 2 is the group that rushes out of the house in the morning to get to work. They only return at night and do all activities at night, so there is no morning peak. The third one has a strong early morning and late night hours. These consumers may be flexible students or elderly retirees who are night owls. Presence of children or stay-at-home parents is indicated by Group-4's almost equivalent morning, afternoon and evening profile. All of this may be validated with further information about the customer.

\noindent The second panel of Figure \ref{fig:combined} shows that month-of-year qualitative clusters are not as distinguishable as hour-of-day. Group 2 is the most distinct and uses the most power during the summer, possibly owing to the use of air conditioners. Group 4 has a flat profile, indicating no significant month-to-month changes. Groups 1 and 3 have heaters on in the winter but consume less energy in the summer. Since gas is not available in all of NSW LGAs, it is possible that customers' heater usage is recorded in electricity rather than gas.

\noindent The third panel of Figure \ref{fig:combined} shows that the wknd-wday groups exhibit no significant changes across clusters, indicating that they may be a nuisance variable for these consumers.

\noindent The plotting scales are not displayed since we want to emphasise comparable shapes rather than scales. A customer in the cluster may have low daily or total energy usage, but their behaviour may be quite similar to a customer with high usage. That places them in the same group.

@@

data_heatmap_moy_group$group <- paste("group", data_heatmap_moy_group$group, sep = "-")

moy_group <- data_heatmap_moy_group %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=group, fill = as.factor(group)), alpha = 0.5) +
  geom_line(aes(y = `50%`, group=group, color = as.factor(group)), size = 1 ) +
  facet_wrap(~group, 
             scales = "free_y", 
             labeller = "label_value",
             nrow = 4) +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("month-of-year") + 
  ylab("demand (in Kwh)") +
  theme_bw() +
   theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) + 
  theme(panel.spacing =unit(0, "lines")) + 
  theme(plot.margin = margin(0, 0, 0, 0, "cm"))  +
   scale_color_manual(legend_title, values = c("#E69F00", "#009E73","#0072B2", "#D55E00")) +
  scale_fill_manual(legend_title, values = c("#E69F00", "#009E73","#0072B2", "#D55E00")) + 
  theme(legend.position = "bottom") +
  theme(panel.spacing =unit(0, "lines")) + 
  theme(axis.text.x = element_text(angle=90, hjust=1, size = 7))
```

@@

p1 <- data_heatmap_wkndwday %>% 
  mutate(customer_id = as.character(customer_id)) %>% 
  left_join(cluster_result, by = c("customer_id" = "id")) %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=customer_id), fill = "lightblue") +
  geom_line(aes(y = `50%`, group=customer_id, color = as.factor(group)), size = 1) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) +
    theme(strip.text = element_text(size = 7, margin = margin(b = 0, t = 0))) + xlab("wknd_wday") + ylab("demand (in Kwh)")  + theme_bw() +
   theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) +
  theme(panel.spacing =unit(0, "lines")) + theme(axis.text.x = element_text(angle=90, hjust=1, size = 7)) + theme(legend.position = "bottom")+ theme(
    strip.text = element_text(size = 8, margin = margin(b = 0, t = 0)))+
  theme(plot.margin = margin(0, 0, 0, 0, "cm") ) +
  scale_fill_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00"))+
  scale_color_manual(values = c("#E69F00", "#009E73","#0072B2", "#D55E00"))+
  theme(legend.position = "bottom")

@@

```{r data-heatmap-wkndwday-group-new}
data_group <- data_pick %>% 
  mutate(customer_id = as.character(customer_id)) %>% 
  left_join(cluster_result, by = c("customer_id" = "id"))

@@

data_heatmap_wkndwday_group$group <- paste("group", data_heatmap_wkndwday_group$group, sep = "-")

wkndwday_group <- data_heatmap_wkndwday_group %>% 
  ggplot(aes(x = category)) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`, group=group, fill = as.factor(group)), alpha = 0.5) +
  geom_line(aes(y = `50%`, group=group, color = as.factor(group)), size = 1 ) +
  facet_wrap(~group, 
             scales = "free_y", 
             labeller = "label_value",
             nrow = 4)+
    #theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) 
    xlab("wknd-wday") + 
  ylab("demand (in Kwh)") +
  theme_bw() +
   theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) + 
  theme(panel.spacing =unit(0, "lines")) + 
  theme(plot.margin = margin(0, 0, 0, 0, "cm"))  +
   scale_color_manual(legend_title, values = c("#E69F00", "#009E73","#0072B2", "#D55E00")) +
  scale_fill_manual(legend_title, values = c("#E69F00", "#009E73","#0072B2", "#D55E00")) + 
  theme(legend.position = "bottom") +
  theme(panel.spacing =unit(0, "lines")) + 
  theme(axis.text.x = element_text(angle=90, hjust=1, size = 7))
```

```{r combined, fig.cap="The distribution of electricity demand for the clusters across hour-of-day. The median is represented by a line and the shaded region represents the area between $25^{th}$ and $75^{th}$ percentile. Each cluster is characterised by unique shape across the granularity it is plotted against. For wknd-wday differences across different groups are not distinct suggesting that it might not be that important a variable to distinguish different clusters. This fact we will be re-established when we see the importance of each granularity throough the parallel coordinate plot."}

combined <- hod_group + moy_group + wkndwday_group & theme(legend.position = "bottom")
combined + plot_layout(guides = "collect")
